---
title: "plots"
author: "Marco Garofalo"
date: "6/18/2021"
output:
  html_document: 
    toc: true
  pdf_document: 
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("plotly")
library("Rose")
require(tikzDevice)
```


## Including Plots in html and pdf

You can also embed plots, for example:


```{r ,results='asis', dev='tikz'}
#gg<- ggplot()+ geom_point(aes(x=c(1,2,3),y=c(1,2,3)  ))
#gg<- ggplot()
start_time <- Sys.time()
source("../R/plot_routines.R")
gg<-  geom_error(ggplot(),x=c(1,2,3),y=c(1,2,3) ,dy=c(0.5,0.5,0.5),
                 color=as.factor(c(1,2,3)),size=as.factor(c(3,2,1)),shape=as.factor(c(1,2,3)),width=0.2, stroke=0.3  )
gg<- gg+scale_shape_manual(values=seq(0,50))
for( i in c(1,2)){
title<-paste('$\\mbox{plot number',i,'}\\chi$')
myplotly(gg, title,'$x_0/a$','a_b', c(0,2),c(0,1.5), to_print=TRUE )
  cat("Important `results='asis'` needed \n\n")
  cat('## Next plot \n\n')
  
}
fig<-myplotly(gg, title="this will be saved in the file figure.pdf",'$x_0/a$','a_b', xrange=c(0,2),yrange=c(0,1.5), to_print=FALSE, save_pdf="figure" )
end_time <- Sys.time()    
end_time - start_time
``` 


# Importan to render plotly inside loop 

The only way to render plotly inside loop is to add this line of code in the Rmarkdown, then you can add a plotly object `fig` inside a loop with `print(htmltools::tagList(fig))` , it is enought to use `include=FALSE` so that there is no
output produced but the code will still run


```{r ,include=FALSE}
df <- data.frame(x = 1:5, y = 1:5)    
f1 <- function(df) {
  gg <- ggplot(df, aes(x,y)) + geom_point()
  assign("ggp", plotly::ggplotly(gg), envir=parent.frame())
  #ggp
  df    # NOT returning a plot
}
res1 <- f1(df)
ggp   # Let knit handle the plot
```


```{r eval=FALSE}
{r ,include=FALSE}
df <- data.frame(x = 1:5, y = 1:5)    
f1 <- function(df) {
  gg <- ggplot(df, aes(x,y)) + geom_point()
  assign("ggp", plotly::ggplotly(gg), envir=parent.frame())
  #ggp
  df    # NOT returning a plot
}
res1 <- f1(df)
ggp   # Let knit handle the plot
```

# Read outfile



```{r ,results='asis', dev='tikz'}
#gg<- ggplot()+ geom_point(aes(x=c(1,2,3),y=c(1,2,3)  ))
#gg<- ggplot()
start_time <- Sys.time()
source("../R/plot_routines.R")
mt<-read_df("example.output")
all_obs<- get_all_corr(mt)

L<- 1 
T<- 1
# gg<- ggplot()
# gg<-plot_corr("E1_0",all_obs,mt,L,T,gg,"no")
# gg<-plot_corr("E1_1",all_obs,mt,L,T,gg,"no")
# gg<-plot_corr("E3_0_vev",all_obs,mt,L,T,gg,"no")
# fig<- myplotly(gg,paste0("meff L",L,"T",T),"t", "y", to_print=TRUE )

df<-add_corr_to_df("E1_0",all_obs,mt,gg)
df<- rbind(df, add_corr_to_df("E1_1",all_obs,mt,gg)  )
df<- rbind(df, add_corr_to_df("E3_0_vev",all_obs,mt,gg)  )
gg<- plot_df_corr_ggplot(df)
fig<- myplotly(gg,paste0("meff L",L,"T",T),"t", "y", to_print=TRUE )

end_time <- Sys.time()    
end_time - start_time
``` 



# Colors

to color automatically in html and pdf use the inline function  colorise or rize
`r colorize("$\\alpha$ is red", "red")` and `r colorize("$\\beta$ is blue", "blue")`

# Formatting error

```{r}
mean_print(3.1572872, 0.8273827368723)
mean_print(3.1572872, 0.8273827368723, digit=1)
mean_print(3.1572872, 0.8273827368723, digit=5)
mean_print(31572872, 8273827368723)
```
## Known issue 0.99999

```{r}
mean_print(3.1572872, 1.99999, digit=1)
mean_print(3.1572872, 0.99999, digit=2)
mean_print(3.1572872, 0.99999, digit=7)
mean_print(3.99999, 1.99999, digit=1)

```
