---
title: "plots"
author: "Marco Garofalo"
date: "6/18/2021"
output:
  html_document: 
    toc: true
  pdf_document: 
    toc: true
---

```{r setup include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("plotly")
library("Rose")
library(knitr)
require(tikzDevice)
```


## Including Plots in html and pdf

You can also embed plots, for example:


```{r ,results='asis', dev='tikz'}
#gg<- ggplot()+ geom_point(aes(x=c(1,2,3),y=c(1,2,3)  ))
#gg<- ggplot()
start_time <- Sys.time()
source("../R/plot_routines.R")
gg<-  geom_error(ggplot(),x=c(1,2,3),y=c(1,2,3) ,dy=c(0.5,0.5,0.5),
                 color=as.factor(c(1,2,3)),size=as.factor(c(3,2,1)),shape=as.factor(c(1,2,3)),width=0.2, stroke=0.3  )
gg<- gg+scale_shape_manual(values=seq(0,50))
for( i in c(1,2)){
title<-paste('$\\mbox{plot number',i,'}\\chi$')
myplotly(gg, title,'$x_0/a$','a_b', c(0,2),c(0,1.5), to_print=TRUE )
  cat("Important `results='asis'` needed \n\n")
  cat('## Next plot \n\n')
  
}
fig<-myplotly(gg, title="this will be saved in the file figure.pdf",'$x_0/a$','a_b', xrange=c(0,2),yrange=c(0,1.5), to_print=FALSE, save_pdf="figure" )
end_time <- Sys.time()    
end_time - start_time
``` 


# Importan to render plotly inside loop 

The only way to render plotly inside loop is to add this line of code in the Rmarkdown, then you can add a plotly object `fig` inside a loop with `print(htmltools::tagList(fig))` , it is enought to use `include=FALSE` so that there is no
output produced but the code will still run


```{r ,include=FALSE}
df <- data.frame(x = 1:5, y = 1:5)    
f1 <- function(df) {
  gg <- ggplot(df, aes(x,y)) + geom_point()
  assign("ggp", plotly::ggplotly(gg), envir=parent.frame())
  #ggp
  df    # NOT returning a plot
}
res1 <- f1(df)
ggp   # Let knit handle the plot
myplotly(ggplot())
```


```{r, eval=FALSE}
{r ,include=FALSE}
df <- data.frame(x = 1:5, y = 1:5)    
f1 <- function(df) {
  gg <- ggplot(df, aes(x,y)) + geom_point()
  assign("ggp", plotly::ggplotly(gg), envir=parent.frame())
  #ggp
  df    # NOT returning a plot
}
res1 <- f1(df)
ggp
myplotly(ggplot())
```

# Read outfile



```{r ,results='asis', dev='tikz'}

start_time <- Sys.time()
source("../R/plot_routines.R")
mt<-read_df("example.output")
all_obs<- get_all_corr(mt)

L<- 1 
T<- 1

df<-add_corr_to_df(string = "E1_0",all_obs=all_obs,mt=mt,df = NULL,
                   log = FALSE, number = NULL,nudge = 0,print_res = TRUE)
df<-add_corr_to_df("E1_1",all_obs,mt,df)
df<- add_corr_to_df("E3_0_vev",all_obs,mt,df, print_res = TRUE)
fit<-get_full_res(string="E3_0_vev",all_obs,mt,number=NULL)
print(fit)
n<- which(all_obs[,"corr"]=="E3_0_vev")
all_obs[n,"chi2.dof"]

#### add annotation not work in plotly
#library(grid)
#grob_5<- grobTree(textGrob( "note $1+1=2$",  x=0.32,  y=0.89, hjust=0,
#                            gp=gpar(col="black", fontsize=40)))
#gg<- gg + annotation_custom(grob_5)
###
gg<- plot_df_corr_ggplot(df)
fig<- myplotly(gg,paste0("meff L",L,"T",T),"t", "y", to_print=TRUE )

end_time <- Sys.time()    
end_time - start_time
``` 

# plotting fits 

```{r, results='asis', warning=FALSE}
source("../R/plot_routines.R")
################################################################################


################################################################################



dir<-"./fit_all/"
namefit<-paste0(dir,"amu_bound_a2_a4_GS_L_Mpi")
file<-paste0(namefit,"_fit_P.dat")
fit<- read_fit_P_file(file)
cat("\n\n")
dt<-make_table_fit_result(fit)
print(dt)
gg<-myggplot()
gg<-plot_fit(basename = namefit, var="afm",data_type = c("TM","OS"), width=1e-4, gg=gg
                 ,               id_color = 5, id_shape = 5,
              # , labelfit = ""
                # ,single_name_for_fit ="fit"
             # , nolabel_for_fit = TRUE
             ,noline=TRUE
               )
fig<-myplotly(gg, "","$a^2[fm]$",
            paste0("$a_\\mu$"), to_print = TRUE)
gg<-myggplot()

gg<-plot_fit(basename = namefit, var="afm",data_type = c("TM","OS"), width=1e-4, gg=gg
                 ,               id_color = 5, id_shape = 5,
              , labelfit = ""
                # ,single_name_for_fit ="fit"
             # , nolabel_for_fit = TRUE
             ,noline=TRUE
               )
fig<-myplotly(gg, "","$a^2[fm]$",
            paste0("$a_\\mu$"), to_print = TRUE)
gg<-myggplot()

gg<-plot_fit(basename = namefit, var="afm",data_type = c("TM","OS"), width=1e-4, gg=gg
                 ,               id_color = 5, id_shape = 5,
              #, labelfit = ""
                 ,single_name_for_fit ="fit"
             # , nolabel_for_fit = TRUE
             ,noline=TRUE
               )
fig<-myplotly(gg, "","$a^2[fm]$",
            paste0("$a_\\mu$"), to_print = TRUE)
gg<-myggplot()

gg<-plot_fit(basename = namefit, var="afm",data_type = c("TM","OS"), width=1e-4, gg=gg
                 ,               id_color = 5, id_shape = 5,
              , labelfit = "zap-"
                # ,single_name_for_fit ="fit"
             # , nolabel_for_fit = TRUE
             ,noline=TRUE
               )


fig<-myplotly(gg, "","$a^2[fm]$",
            paste0("$a_\\mu$"), to_print = TRUE)
```


```{r,results='asis'}


dir <- "/home/garofalo/analysis/g-2_new_stat/fit_all/"
namefit <- paste0(dir, "afpi_cov")
file <- paste0(namefit, "_fit_P.dat")
fit <- read_fit_P_file(file)
cat("\n\n")
dt <- make_table_fit_result(fit)
print(dt)
gg <- myggplot(repeat_color = 1)
gg <- plot_fit(
  basename = namefit,
  var = "xi",
  id_x = 5,
  data_type = c("A", "B", "C", "D", "E", "B", "C", "D"),
  width = 1e-4,
  gg = gg, ,
  labelfit = "",
    # , single_name_for_fit = "fit"
   #, nolabel_for_fit = TRUE
  , noline = TRUE
)
gg <- gg + geom_vline(xintercept = 0.00678723)
fig <- myplotly(gg, "", "$\\xi$", "$af_\\pi$", to_print = TRUE)
```

# Colors

to color automatically in html and pdf use the inline function  colorise or rize
`r colorize("$\\alpha$ is red", "red")` and `r colorize("$\\beta$ is blue", "blue")`

# Formatting error

```{r}
mean_print(3.1572872, 0.8273827368723)
mean_print(3.1572872, 0.8273827368723, digit=1)
mean_print(3.1572872, 0.8273827368723, digit=5)
mean_print(31572872, 8273827368723)
```

```{r}
mean_print(3.1572872, 1.99999, digit=1)
mean_print(3.1572872, 1.99999, digit=2)
mean_print(3.1572872, 0.99999, digit=2)
mean_print(3.1572872, 0.99999, digit=7)
mean_print(3.99999, 1.99999, digit=1)

```
